KidsAIR: initial exposure analysis

### 2020-04-10 exposure_initial_analysis.Rmd
new exposure analysis

```{r, message=FALSE}
library(tidyverse)
library(readxl)
library(naniar)
library(lubridate)
library(broom)
library(broom.mixed)
library(zoo)
library(lme4)
library(lmerTest)
library(ggmap)
```

@@

>>>>

```{r, message=FALSE}
library(readxl)
library(naniar)
library(lubridate)
library(broom)
library(broom.mixed)
library(zoo)
library(lme4)
library(lmerTest)
library(ggmap)
library(mctest)
library(GGally)
library(tidyverse)
```

@@

# Run tests for multicollinearity between different covariates
Goal is to check for vars that have a lot of overlap and eliminate some from
consideration to include in models

First, use `mctest` package to check for multicollinearity among similar variables
https://cran.r-project.org/web/packages/mctest/mctest.pdf

Notes on multicollinearity:

https://datascienceplus.com/multicollinearity-in-r/ 
https://www.theanalysisfactor.com/eight-ways-to-detect-multicollinearity/

```{r}
# Filter data for specific variables; select pm variable
pm_mean_sampling_period <- exposure_analysis_data_short %>% 
  filter(winter_id == 1) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  select(pm_mean_sampling_period, income_3level, residents_smoke) %>% 
  mutate_all(as.numeric) %>% 
  na.exclude() %>% 
  select(pm_mean_sampling_period)

# Filter data for specific variables; select predictor variables
other_vars <- exposure_analysis_data_short %>% 
  filter(winter_id == 1) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  select(pm_mean_sampling_period, income_3level, residents_smoke) %>% 
  mutate_all(as.numeric) %>% 
  na.exclude() %>% 
  select(-pm_mean_sampling_period)

# Use `omcdiag` to assess overall multicollinearity
omcdiag(other_vars, pm_mean_sampling_period)

# Use `imcdiag` to assess multicollinearity between individual variables
imcdiag(other_vars, pm_mean_sampling_period)

# Specify a method to assess
imcdiag(other_vars, pm_mean_sampling_period, method = "Fi")
```

# Initial variables to use for model selection (these have less overlap):
Demographics: income_3level, total_residents_2level, residents_smoke
Home Characteristics: home_type_2level, home_floors_2level, stove_age_3level,
                      chimney_clean_3level, home_mold, home_fireplace
Home Activity: home_act_gas, home_act_smoking
Others (make some categorical): amb_pm_24hr, mean_temp, sums_mean_sampling_day, 
       moisture_closest, stove_grade_3level

# Also try individual chi-square tests and correlations b/w two vars

```{r}
test_data <- exposure_analysis_data_medium %>% 
  filter(winter_id == 1) %>% 
  filter(!is.na(pm_mean_sampling_day))

chisqu_results <- chisq.test(test_data$home_floors_2level, 
                             test_data$home_windows_2level)
chisqu_results

cor_results <- cor.test(test_data$temp_indoor_max, 
                        test_data$mean_temp)
cor_results
```

If variables have very high overlap, then only use the one with the strongest
association with PM for consideration in the model.

Once variables are narrowed down, use best subsets selection (exposure_models.RMD) 
to help inform a final model.

Run sensitivity analyses to see if adding other variables back in makes a difference.
